Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-09-24 manuscript.qmd
add paragraph to the "implications" section

# Results: Prediction of Risk for Occult Disease

@@

## Limitations and Future Work

>>>>

# Results: Prediction of Risk for Occult Disease {#sec-results-risks}

@@

In essence, this is a summary of the results in @sec-sec-results-risks. However, it should be considered in light of the limitations outlined in @sec-discussion-limitations below.

## Limitations and Future Work {#sec-discussion-limitations}
